### 2014-09-26 ms/ms.Rmd
Incorporate feedback from Ishihara. Clsoes #174.

D.S. Falster, A. Vårhammer and D.R. Barneche were employed on an ARC discovery grant to Falster (DP110102086) and a UWS start-up grant to R.A. Duursma. R.G. FitzJohn was supported by the Science and Industry Endowment Fund (RP04-174). M.I. Ishihara was supported by the Environmental Research and Technology Development Fund (S-9-3) of the Ministry of the Environment, Japan. We thank Takahiro Inoue, Hayato Aoyama and Shin-ichiro Aiba for valuable assistance. In addition, the authors thank the following people for contributions to the following studies:

```{r,results="asis",echo=FALSE, message=FALSE}

getAcknowledgments <- function(studyName) {
  metadata  <-  readStudyFile(studyName, "studyMetadata.csv")
  i <- match("Acknowledgements",metadata$Topic)
  out <- ""
  if(!is.na(i))
    out <- sprintf("- %s: %s.\n", studyName, metadata$Description[i])
  out
}
writeLines(paste(sapply(unique(data$studyName), getAcknowledgments), collapse= ""))
```

>>>>

**Compilers:** D.S. Falster, A. Vårhammer and D.R. Barneche were employed on an ARC discovery grant to Falster (DP110102086) and a UWS start-up grant to R.A. Duursma. R.G. FitzJohn was supported by the Science and Industry Endowment Fund (RP04-174). M.I. Ishihara was supported by the Environmental Research and Technology Development Fund (S-9-3) of the Ministry of the Environment, Japan. We thank Takahiro Inoue, Hayato Aoyama and Shin-ichiro Aiba for valuable assistance.

In addition, we thank the following people for contributions to the following studies:
```{r,results="asis",echo=FALSE, message=FALSE}
getAcknowledgments <- function(studyName) {
  metadata  <-  readStudyFile(studyName, "studyMetadata.csv")
  i <- match("Acknowledgements",metadata$Topic)
  out <- ""
  if(!is.na(i))
    out <- sprintf(" **%s:** %s;", studyName, metadata$Description[i])
  out
}
writeLines(paste(sapply(unique(data$studyName), getAcknowledgments), collapse= ""))
```
.
